Supplementary Materials

### 2020-05-27 analysis/analysis.Rmd
Fixed subgroup comparisons?

df %>% gather("measurement", "number", -p) %>%
  mutate(proportion = number/64) %>%
  ggplot(aes(x = p, y = proportion, colour = measurement)) + geom_point() + geom_path() +
  theme_minimal() + ggthemes::scale_color_ptol(labels = c("primary EEG", "sensor control EEG", "harmonic control EEG", "psychophysical threshold")) +
  xlab("probability of difference given data") + ylab("proportion of subgroup comparisons")
```

>>>>

filter(df, p == 0.95)

df %>% gather("measurement", "number", -p) %>%
  mutate(proportion = number/nrow(subgroups)) %>%
  ggplot(aes(x = p, y = proportion, colour = measurement)) + geom_point() + geom_path() +
  theme_minimal() + ggthemes::scale_color_ptol(labels = c("primary EEG", "sensor control EEG", "harmonic control EEG", "psychophysical threshold")) +
  scale_y_continuous(limits = c(0, 1)) +
  xlab("probability of difference given data") + ylab("proportion of subgroup comparisons")
```
